\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-09-19 demystify.tex
prof references

If you don't know the professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste names, so no need to do so,  just Prof. or Dr. Lastname.
Moreover, if you don't know the prof., do not use Mr. or Mrs., or Firstname. To me it seems a bit disrespectful. As you know that prof. better and depends on their preference, you may call them by their firstname. Many students call me \emph{Dr. Vu}, which I find a bit amusing but am totally fine with it (and Vu is way easier to pronounce than Nguyen).

Note that at some universities, especially those that do not offer PhD studies, will use the formal \textbf{Dr.} title, i.e., Dr. Lastname.  So just observe and follow how it is done at your place.  Also note that some faculty might not have a Ph.D., so they might not be Dr.  In that case, you can use Prof. Lastname.

@@

\section{Cultural Differences and Tips}

>>>>

If you don't know the professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste names, so no need to do so,  just Prof. or Dr. Lastname.
Moreover, if you don't know the prof., do not use Mr. or Mrs., or Firstname. To me it seems a bit disrespectful. As you know that prof. better and depends on their preference, you may call them by their firstname.  For example, my students and colleague call me Vu. Some students call me \emph{Dr. Vu}, which I find a bit amusing but am totally fine with it.

Note that at some universities, especially those that do not offer PhD degrees, will use the formal \textbf{Dr.} title, i.e., Dr. Lastname.  So just observe and follow how it is done at your place.  Also note that some faculty might not have a Ph.D. and so you can use Prof. Lastname instead.

A related topic is to consider is how to refer to a professor you know. Here, because you are already familiar with these individuals, you can informally use their firstname (or Dr./Prof., if you want to be formal) as mentioned above. You can also include their institution if it makes it more precise.  For example, I did my postdoc with Jeff Foster at Univ. of Maryland.   Do not include ranking (e.g., Assistant, Associate, Scientist, ...) when referring to someone. I see many students, especially Vietnamese, include a lengthy title of people they know, e.g., my advisors are Asst. Prof. X and Assoc. Prof. Y., and I also collaborate with ACM Distinguished Scientist Z.  This is \emph{not necessary} and makes it look like you're trying to show off your connections. In short, these nuances represent some cultural differences that you may encounter and will gradually adapt to (more on cultural differences in \S\ref{sec:cultural}).

@@

\section{Cultural Differences and Tips}\label{sec:cultural}
